Analysis of gene regulatory properties underlying trait pleiotropy

### 2022-10-18 presentation_gold2022_paris/presentation_gold2022_paris.tex
ENH

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{frame}
%\frametitle{Which are the most pleiotropic variants?}

@@

%\end{frame}

@@

\begin{columns}
\begin{column}{0.32\textwidth}
    \begin{center}
\includegraphics[width=\textwidth]{/home/gonzalez/Repositories/gwas2eqtl_pleiotropy/out/gwas418/pval_5e-08/r2_0.1/kb_1000/window_1000000/pltsctr_x_per_rsid_y_gwas.py/count_per_rsid_chr5_start131912097_end132802472_categories7.png}
     \end{center}
\end{column}
\begin{column}{0.32\textwidth}
    \begin{center}
\includegraphics[width=\textwidth]{/home/gonzalez/Repositories/gwas2eqtl_pleiotropy/out/gwas418/pval_5e-08/r2_0.1/kb_1000/window_1000000/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr5_start131912097_end132802472_categories7.png}
     \end{center}
\end{column}
\begin{column}{0.32\textwidth}
    \begin{center}
\includegraphics[width=\textwidth]{/home/gonzalez/Repositories/gwas2eqtl_pleiotropy/out/gwas418/pval_5e-08/r2_0.1/kb_1000/window_1000000/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr5_start131912097_end132802472_categories7.png}
     \end{center}
\end{column}
\end{columns}
%
\vfill
%
Neighboring variants show similar pleiotropy.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{frame}
%\frametitle{Diseases?}

@@

@@

\begin{columns}
\begin{column}{0.32\textwidth}
    \begin{center}
\includegraphics[width=\textwidth]{/home/gonzalez/Repositories/gwas2eqtl_pleiotropy/out/gwas418/pval_5e-08/r2_0.1/kb_1000/window_1000000/pltsctr_x_per_rsid_y_gwas.py/count_per_rsid_chr5_start131912097_end132802472_categories7.png}
     \end{center}
\end{column}
\begin{column}{0.32\textwidth}
    \begin{center}
\includegraphics[width=\textwidth]{/home/gonzalez/Repositories/gwas2eqtl_pleiotropy/out/gwas418/pval_5e-08/r2_0.1/kb_1000/window_1000000/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr5_start131912097_end132802472_categories7.png}
     \end{center}
\end{column}
\begin{column}{0.32\textwidth}
    \begin{center}
\includegraphics[width=\textwidth]{/home/gonzalez/Repositories/gwas2eqtl_pleiotropy/out/gwas418/pval_5e-08/r2_0.1/kb_1000/window_1000000/pltsctr_x_per_rsid_y_etissue.py/count_per_rsid_chr5_start131912097_end132802472_categories7.png}
     \end{center}
\end{column}
\end{columns}

\begin{center}
\includegraphics[width=\textwidth]{/home/gonzalez/Repositories/gwas2eqtl_pleiotropy/presentation_gold2022_paris/fig/chr5_131912097_132802472.png}
\end{center}

\small
\begin{itemize}
\item The cytokine locus: chr5:131,912,097-132,802,472. Genes IL3, IL4, IL5, ...
\item Diseases: Allergy,Autoimmune dis.,Cancer of breast,Circulatory sys. dis.,Hypertension,Respiratory system dis.
\item For instance: rs2522051 regulates 12 e-genes in 23 e-tissues
\end{itemize}
\normalsize
